\mbox{Verifying Imperative Higher-Order Programs}

### 2009-10-08 papers/esop2010/main.tex
go

%TODO overfull boxes

@@

The store types $\efft{ε}$ describe a portion of the store and are basically
mappings from region variables to values. The domain of the mapping is the
effect $ε$, where effect variables stand for unknown parts of the domain. To
dea with objects of these types, we introduce three symbols
\begin{eqnarray*}
  \oplus &:&∀ e1 e2 . \efft{ e1 } -> \efft{ e2 } -> \efft { e1  e2 }\\
  |_{ε} &:& ∀e. \efft{ e ε } -> \efft{ ε }\\
  {\tt !!} & : & ∀αρe. α~\refml_ρ -> \efft{ ρ e } -> α.
\end{eqnarray*}
The first one denotes a combining operation for stores; the resulting store
contains all the mappings of the second store, as well as all the mappings of
the first one, as long as they are not present in the second one. The second
operations is indexed by an effect and it restricts a store to a certain
effect. Finally, the double bang {\tt !!} is the logic equivalent to the
lookup operator {\tt !}. It is pure and it is always with respect to a certain
state.

>>>>

@@

The store types $\efft{ε}$ describe a portion of the store and are basically
mappings from references to values. The domain of the mapping is the
effect $ε$, where effect variables stand for unknown parts of the domain. To
deal with objects of these types, we introduce three symbols
\begin{eqnarray*}
  \oplus &:&∀ e1 e2 . \efft{ e1 } -> \efft{ e2 } -> \efft { e1  e2 }\\
  |_{ε} &:& ∀e. \efft{ e ε } -> \efft{ ε }\\
  {\tt !!} & : & ∀αρe. α~\refml_ρ -> \efft{ ρ e } -> α.
\end{eqnarray*}
The first one denotes a combining operation for stores; the resulting store
contains all the mappings of the second store, as well as all the mappings of
the first one, as long as they are not present in the second one. The second
operations is indexed by an effect and it restricts a store to a certain
effect. Finally, the double bang {\tt !!} is the logic equivalent to the
lookup operator {\tt !}. It is pure and it is always with respect to a certain
state.
